\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{setspace}
\doublespacing
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{FEA Major Project Draft Report}
\author{Alex Moraitis\\Z5017180}
\date{21 September 2017}


\begin{document}
\maketitle

\begin{abstract}
This document outlines the finite element simulation process conducted to determine the stress and deformation of a 3D printed Hexapod leg. This is the first step in optimisation of the concept design before manufacturing. The purpose of this study is directed at hobbyist that want to alter components of their products to change functionality or physical capabilities. The first step of the modelling process is the analyse simple 3D model of the leg that consist of a single body. These results from this simulation became the standard and will be used for comparison of future optimised models. To validate these results, convergence tests were conducted using ANSYS built in functions.
\end{abstract}

\newpage
\tableofcontents
\newpage

\section{Introduction}
3D printing is a manufacturing process from which solid objects can be made from digital files. This is achieved by repeatedly melting and laying down material in layers until the object is formed. This process is becoming popular within households as 3D printers are gradually becoming commercially affordable. The standard commercial printer is typically able to print using either Polylactic Acid (PLA) or Acrylonitrile Butadiene Styrene (ABS). Even though printers can do both thermoplastics, there is a significant difference in the physical properties they exhibit. ABS has a  significantly higher yield strength than PLA, however its print quality if not as sharp as that of the PLA. Since the hexapod leg is to experience impact forces, ABS was chosen due to  being much stronger, more flexible and machinable compared to PLA.

Since thermoplastics are melted and then layered, they display material properties close similar to composites. They become very susceptible to cracking if printing conditions are not met or at stress concentrators. Current simulation programs, like ANSYS, have been developed to accurately analyse failure points and maximum stresses of such composite plastic materials.
\newpage

\section{Project Requirements and Plan}

\subsection{How to include Figures}

First you have to upload the image file from your computer using the upload link the project menu. Then use the includegraphics command to include it in your document. Use the figure environment and the caption command to add a number and a caption to your figure. See the code for Figure \ref{fig:frog} in this section for an example.


\subsection{How to add Comments}

Comments can be added to your project by clicking on the comment icon in the toolbar above. % * <john.hammersley@gmail.com> 2016-07-03T09:54:16.211Z:
%
% Here's an example comment!
%
To reply to a comment, simply click the reply button in the lower right corner of the comment, and you can close them when you're done.

Comments can also be added to the margins of the compiled PDF using the todo command\todo{Here's a comment in the margin!}, as shown in the example on the right. You can also add inline comments:

\todo[inline, color=green!40]{This is an inline comment.}

\subsection{How to add Tables}

Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. 


\subsection{How to write Mathematics}

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
\[S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i\]
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.


\subsection{How to create Sections and Subsections}

Use section and subsections to organize your document. Simply use the section and subsection buttons in the toolbar to create them, and we'll handle all the formatting and numbering automatically.

\subsection{How to add Lists}

You can make lists with automatic numbering \dots

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}
\dots or bullet points \dots
\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}

\subsection{How to add Citations and a References List}

You can upload a \verb|.bib| file containing your BibTeX entries, created with JabRef; or import your \href{https://www.overleaf.com/blog/184}{Mendeley}, CiteULike or Zotero library as a \verb|.bib| file. You can then cite entries from it, like this: \cite{greenwade93}. Just remember to specify a bibliography style, as well as the filename of the \verb|.bib|.

You can find a \href{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}{video tutorial here} to learn more about BibTeX.

We hope you find Overleaf useful, and please let us know if you have any feedback using the help menu above --- or use the contact form at \url{https://www.overleaf.com/contact}!

\bibliographystyle{alpha}
\bibliography{sample}

\end{document}